Extended Abstract

### 2021-05-12 paper/paper.tex
Change the title to two lines
Shorten (sub)section autoref names
Add section with contributions

@@

\title
[Co-Contextual Type Inference for the Linear \Picalc{} in Agda]
{Co-Contextual Type Inference \\ for the Linear \Picalc{} \\ in Agda}
\subtitle{(Extended Abstract)}

@@

(Variables are black, \textcolor{blue}{types are blue}, \textcolor{olive}{constructors are olive green}, \textcolor{gray}{functions are gray}, and we are sorry this is not a wee poem.)

>>>>

\renewcommand*{\sectionautorefname}{\S\!\!\,}
\renewcommand*{\subsectionautorefname}{\S\!\!\,}

@@

\title
[Co-Contextual Type Inference for the Linear \Picalc{} in Agda]
{Co-Contextual Type Inference \\ for the Linear \Picalc{} in Agda}
\subtitle{(Extended Abstract)}

@@

\paragraph{Contributions}
\begin{itemize}
  \item We break down typing inference into constraint collection and constraint resolution and state clear soundness and completeness theorems for both phases.
  \item We are working on mechanising the proofs for these theorems in Agda. We have already shown the soundness of constraint collection and the soundness of equality constraint resolution (adapting McBride's work \cite{McBride03} to deal with intrinsically kinded terms).
\end{itemize}

(Variables are black, \textcolor{blue}{types are blue}, \textcolor{olive}{constructors are green}, \textcolor{gray}{functions are gray}, and we are sorry this is not a poem.)
